---
title: "Homework 5"
author: "Liner Ge"
date: "2020/11/14"
output: github_document
---

```{r setup}
library(tidyverse)
library(rvest)

knitr::opts_chunk$set(
  fig.height = 8,
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data.
```{r}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
    
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit

```{r}
aggregate_df =
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )

```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>%  filter(city_state == "Baltimore_MD") %>% pull(hom_total)
  
) %>% 
  broom::tidy()

```

Try to iterate...

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~ prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~ broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests)
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Problem 2

Clean the data

```{r}
tidy_df = 
  tibble(
    files = list.files(path = "data/data2", full.names = TRUE) 
         ) %>% 
  mutate(
    data = purrr::map(.x = files, read_csv)
  ) %>% 
  unnest(data) %>% 
  mutate(arm_id = str_extract_all(files, "(exp_\\d+|con_\\d+)")) %>% 
  select(-files) %>% 
  relocate(arm_id) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) %>% 
  mutate_at(vars(week), as.numeric) %>% 
  unnest(arm_id) 

tidy_df %>% knitr::kable()
```

Make a spaghetti plot

```{r}
tidy_df %>%
  mutate(group = case_when(
    str_detect(arm_id,"con") ~ "Control",
    str_detect(arm_id,"exp") ~ "Experimental"
  )) %>% 
  ggplot(aes(x = week,
             y = observations)) +
  geom_path(aes(color = group,
                group = group),
            alpha = 0.5) +
  labs(
    x = "Number of week",
    y = "Observation value",
    title = "Observations on each subject over time"
    )

```

According to the plot, the observation value of experimental group is relatively stable over the 8 weeks; the observation value of control group kept increasing over the 8 weeks. The value of control group is higher than the value of experimental group.
