---
title: "Homework 5"
author: "Liner Ge"
date: "2020/11/14"
output: github_document
---

```{r setup}
library(tidyverse)
library(rvest)
set.seed(1)

knitr::opts_chunk$set(
  fig.height = 8,
  fig.width = 8,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

Read in the data.
```{r}
homicide_df = 
  read_csv("data/homicide-data.csv") %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    )
    
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

Let's look at this a bit

```{r}
aggregate_df =
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  )

```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>%  filter(city_state == "Baltimore_MD") %>% pull(hom_total)
  
) %>% 
  broom::tidy()

```

Try to iterate...

```{r}
results_df = 
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~ prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~ broom::tidy(.x))
  ) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests)
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 1))

```

## Problem 2

Clean the data

```{r}
tidy_df = 
  tibble(
    files = list.files(path = "data/data2", full.names = TRUE) 
         ) %>% 
  mutate(
    data = purrr::map(.x = files, read_csv)
  ) %>% 
  unnest(data) %>% 
  mutate(arm_id = str_extract_all(files, "(exp_\\d+|con_\\d+)")) %>% 
  select(-files) %>% 
  relocate(arm_id) %>% 
  pivot_longer(
    week_1:week_8,
    names_to = "week",
    names_prefix = "week_",
    values_to = "observations"
  ) %>% 
  mutate_at(vars(week), as.numeric) %>% 
  unnest(arm_id) 

tidy_df %>% knitr::kable()
```

Make a spaghetti plot

```{r}
tidy_df %>%
  mutate(group = case_when(
    str_detect(arm_id,"con") ~ "Control",
    str_detect(arm_id,"exp") ~ "Experimental"
  )) %>% 
  ggplot(aes(x = week,
             y = observations)) +
  geom_path(aes(color = group,
                group = group),
            alpha = 0.5) +
  labs(
    x = "Number of week",
    y = "Observation value",
    title = "Observations on each subject over time"
    )

```

According to the plot, the observation value of experimental group is relatively stable over the 8 weeks; the observation value of control group kept increasing over the 8 weeks. The value of control group is higher than the value of experimental group.

## Problem 3

T-test, when mu = 0

```{r}
sim_t = function(n = 30, mu = 0, sigma = 5) {
     x = rnorm(n, mean = mu, sd = sigma)
     t_test = t.test(x, conf.int = 0.95) %>% broom::tidy()
     
     t_test
  }

output = vector("list", 5000)
for (i in 1:5000) {
  output[[i]] = sim_t()
}

output %>% bind_rows() %>% head()

```

A plot showing the power of the test for different true mu
```{r}
sim_mu = function(set){
  output = vector("list", 5000)
  for (i in 1:5000) {
     output[[i]] = sim_t(mu = set)
     }
  power = 
    output %>% 
    bind_rows() %>% 
    janitor::clean_names() %>% 
    select(estimate, p_value) %>% 
    filter(p_value < 0.05) %>% 
    count()
  
  power
}

power_of_test =
  tibble(
    sample_mu = c(1, 2, 3, 4, 5, 6),
    reject_time = map(sample_mu, sim_mu)
  ) %>%  
  unnest(reject_time) %>% 
  mutate(t_power = n/5000)

power_of_test %>% 
ggplot(aes(x = sample_mu, y = t_power)) +
  geom_point(aes(color = sample_mu), alpha = .5, size = 3) +
  geom_smooth(alpha = .5, size = 0.5) +
  labs(
    x = "The true value of μ",
    y = "The power of the test",
    title = "The power of the test for different true mu"
    )

```

According to this plot, as the effect size increases, the power increases. When the true mu equals to 5, the power reaches 1.



```{r}
sim_mu_hat = function(n = 30, mu = 0, sigma = 5) {
     sim_data = tibble(
                           x = rnorm(n, mean = mu, sd = sigma),
                    )
     
     sim_t_test = t.test(pull(sim_data,x), conf.int = 0.95) %>% 
              broom::tidy() %>% 
              janitor::clean_names() %>% 
              select( p_value)
     
     
     sim_data %>% 
     summarize(
      mu_hat_all = mean(x),
      mu_hat_rej = case_when(
        pull(sim_t_test, p_value) < 0.05 ~ mean(x),
        pull(sim_t_test, p_value) >= 0.05 ~ as.numeric("")
      )
    )
  }


compare_all_reject = function(set){
  output_mu_hat = vector("list", 5000)
  for (i in 1:5000) {
     output_mu_hat[[i]] = sim_mu_hat(mu = set)
     }
  
  output_mu_hat %>% 
    bind_rows() %>% 
    summarize(
      all_sample = mean(mu_hat_all, na.rm = T),
      reject_sample = mean(mu_hat_rej, na.rm = T)
    )
  }

mean_muhat =
  tibble(
    true_mu = c(1, 2, 3, 4, 5, 6),
    hat = map(true_mu, compare_all_reject)
  ) %>%  
  unnest(hat) %>% 
  pivot_longer(
    all_sample:reject_sample,
    names_to = "samples",
    values_to = "average_estimate"
  )

mean_muhat %>% 
ggplot(aes(x = true_mu, y = average_estimate, group = samples)) +
  geom_point(aes(color = samples), alpha = .5, size = 2) +
  geom_smooth(aes(color = samples), alpha = .5, size = 0.5) +
  labs(
    x = "The true value of μ",
    y = "The average estimate of μ^",
    title = "Compare the average estimate of μ^ of all sample and reject-null-sample"
    )


```

According to this plot, for all true μ, average estimate of μ^ is equal to the true value of μ. When μ equals to 3, 4, 5, or 6, the sample average of μ^ across tests for which the null is rejected approximately is equal to the true value of μ. Because when μ is close to 0, the number of samples for which the null was rejected decreases and the μ^ of these samples would be far away from 0, which is also far away from μ. Similarly, when μ is away from 0, as for μ=5 and μ=6, for all samples, the null was rejected. Thus, the sample average of μ^(rejected) is equal to the sample average of μ^(all), which equals to true μ.